\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-21 notes/2loopNLSM.tex
Fixed scaling on automorphism diagram equations.
Cleaned up end-of-graph-symmetries comment.

Every numerator is required to respect all of the symmetries (or
automorphisms) of its associated graph.  Graph symmetries are an
avatar of Bose symmetry.  For a pure ansatz construction it is very
reasonable to impose graph symmetries, but color-kinematics duality at
tree-level is often achieved at the expense of manifest Bose symmetry
\cite{Cheung:2016prv, Cheung:2021zvb, Brandhuber:2021bsf,
  Edison:2020ehu}.  In an ansatz construction graph symmetries are
imposed for \emph{every} graph, not just the basis graphs.
For example, the symmetries of the crossed box are spanned by,
\nhp{Alex, fix the scaling to get the boxes to fit}
\be
\CrossedBoxGraphSym{1}{2}{3}{4}\!\! \sim\!\! \CrossedBoxGraphSym{2}{1}{3}{4} 
\text{ and }
\CrossedBoxGraphSym{1}{2}{3}{4} \!\!\sim\!\! \CrossedBoxGraphSym{2}{1}{4}{3}
\ee
%\ace{is there a reason we commented out this diagram?} \jm{You can try
 % either one.  I liked the one I left in better.}  For example, the
%symmetries of the crossed box
%\begin{equation}
%\CrossedBoxGraphSym{1}{2}{3}{4}
%\end{equation}
which are just functional relabelings of external legs, $\{1234\} \to \{2134\}$ and $\{1234\} \to \{1243\}$.
In general, internal edge labels must be tracked as well.
Furthermore, care must be taken with the signs in a symmetry relation.
To compensate for the antisymmetric color factors, $f^{abc}$, graph
vertices are all totally antisymmetric and hence have signs built into
their orientations.  Once imposing symmetry relations, the crossed box can be expressed in terms of the double box
and penta-triangle, thus imposing non-trivial constraints on the
ansatz. 
\nhp{Someone add in comment here about how symmetry relations imposes constraints of jacobi from equation above}.
%\ace{I'm not quite sure why the signs are mentioned in the
%  previous sentence?}

>>>>

Every numerator is required to respect all of the symmetries (or
automorphisms) of its associated graph.  Graph symmetries are an
avatar of Bose symmetry.  For a pure ansatz construction it is very
reasonable to impose graph symmetries, but color-kinematics duality at
tree-level is often achieved at the expense of manifest Bose symmetry
\cite{Cheung:2016prv, Cheung:2021zvb, Brandhuber:2021bsf,
  Edison:2020ehu}.  In an ansatz construction graph symmetries are
imposed for \emph{every} graph, not just the basis graphs.
For example, the symmetries of the crossed box are spanned by,
\begin{equation}
\scalebox{0.8}{\CrossedBoxGraphSym{1}{2}{3}{4}}\!\! \sim\!\! \scalebox{0.8}{\CrossedBoxGraphSym{2}{1}{3}{4}}
\text{ and }
\scalebox{0.8}{\CrossedBoxGraphSym{1}{2}{3}{4}} \!\!\sim\!\! \scalebox{0.8}{\CrossedBoxGraphSym{2}{1}{4}{3}}
\end{equation}
% \ace{is there a reason we commented out this diagram?} \jm{You can try
 % either one.  I liked the one I left in better.}  For example, the
%symmetries of the crossed box
%\begin{equation}
%\CrossedBoxGraphSym{1}{2}{3}{4}
%\end{equation}
which are just functional relabelings of external legs,
$\{1234\} \to \{2134\}$ and $\{1234\} \to \{1243\}$.  In general,
internal edge labels must be tracked as well.  Furthermore, care must
be taken with the signs in a symmetry relation.  To compensate for the
antisymmetric color factors, $f^{abc}$, graph vertices are all totally
antisymmetric and hence have signs built into their orientations.
When used in conjuction with the Jacobi relations, \eg
\cref{eq:TwoLoopJacobiOne}, the symmetry constraints of non-basis
graphs still impose conditions on the basis ansatz.  In fact, since
the symmetry properites of a graph are directly linked with
transformations of its color dressing, the resulting constraints can
be thought of as a subclass of the \emph{boundary} Jacobi relations.
